Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-16 doc/GMP2015/s07_problempinning.tex
Fixed a few typos

% \end{subfigure}
\caption{(a) is an orignal body-pin qusec. (b) is the corresponding body-bar qusec explained in Definition \ref{def:body-pin}. (c) is the 1 dof DR plan for the qusec. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the node in the second level. (d) is the result of adding one such body tot he bold-faced node.}

@@

\begin{theorem}
    There is a quadratic algorithm for the 1 dof and 2 dof optimal completion problem of Seciton \ref{sec:recomb} for body-pin and multi-triangle-pin qusecs.
\end{theorem}

@@

    For the 2 dof case, we can do something very similar, except instead of pinning a single body 2 times to a node, we can pin another body 2 times to a node. These can be the same node, and if it is the same node, we can find a wellconstrained DR plan in quadratic time, we would just be doing the same thing as the 1 dof case.
\end{proof}

>>>>

% \end{subfigure}
\caption{(a) is a 1 dof body-pin qusec. (b) is the corresponding body-bar qusec explained in Definition \ref{def:body-pin}. (c) is the 1 dof DR plan for the qusec. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the node in the second level. (d) is the result of adding one such body tot he bold-faced node.}

@@

\begin{theorem}
    There is a quadratic algorithm for the 1 dof optimal completion problem of Seciton \ref{sec:recomb} for body-pin and multi-triangle-pin qusecs.
\end{theorem}

@@

    For the multi-triangle pin qusecs, we can do the same thing except we need to add a single triangle to one of the nodes to cause it to become isostatic.

    % For the 2 dof case, we can do something very similar, except instead of pinning a single body 2 times to a node, we can pin another body 2 times to a node. These can be the same node, and if it is the same node, we can find a wellconstrained DR plan in quadratic time, we would just be doing the same thing as the 1 dof case.
\end{proof}

\begin{theorem}
    There is a \textcolor{red}{$O(?)$} algorithm for the 1 dof optimal completion problem of Seciton \ref{sec:recomb} for body-pin and multi-triangle-pin qusecs.
\end{theorem}

\begin{proof}
    We can do a similar algorithm to the 1 dof case, except we constrain a given node 2 times (by adding 2 triangles or 2 bodies and 4 pins). This causes the nodes along the path to the given node to become well-constrained while all others will be underconstrained. Thus, our DR plan will have the same size as the 1 dof case. This is still a quadratic algorithm
\end{proof}

An open question remains as to the complexity of the optimal completion problem when there are more than 2 dofs. For higher number of dofs, the $(l,k)$ characterization is no longer matroidal.
